\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

\begin{document}
\author{Quiz 3 - Basic Simulation}
\title{CMPE 211 - Data Structures and Algorithms}
%\setlength\headheight{26pt} 




\date{}
\maketitle
\setcounter{secnumdepth}{0}
You are given simpleAgentQuiz.java code in which a population of $N$ agents
interact with each other during a given period of time. 
Agents have memory which is implemented as an \textbf{unordered array}.
At each time step, two random agents are selected to interact. 
Interaction takes place as giving and taking recommendations among selected agents.
Recommendation is a simple operation which returns a random item from the memory.


\begin{enumerate}
\item Fill the following functions in the code.
\begin{itemize}
\item know(item)  $\;\;$ : \emph{does item exist in the memory, if so return its index.}
\item learn(item) $\;\;\;$: \emph{add \textbf{unknown} item to a random place in the memory}
\item recommend() : \emph{return a random item from the memory}
\end{itemize}

\item Write a new java program, based on the given code, that uses \textbf{an ordered array} for the representation of memory.
\begin{itemize}
\item know(item)  $\;\;$ : \emph{does item exist in the memory, if so return its index.}
\item learn(item) $\;\;\;$: \emph{add \textbf{unknown} item to its \textbf{correct} place}
\item recommend() : \emph{return random item \textbf{from the range $[M/2,M]$}}
\end{itemize}

\item Compare running time for the following operations
\begin{table}[htp]
%\caption{default}
\begin{center}
\begin{tabular}{c|c|c}
 & ordered & unordered\\
 \hline
\hline
know(item) & &\\
\hline
learn(item) & &\\
\hline
recommend() & &\\
\end{tabular}
\end{center}
%\label{default}
\end{table}%


\end{enumerate}
\end{document}
