% !TEX encoding = UTF-8 Unicode
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx, url}

\begin{document}
\author{Project - Recommender Systems From Scratch}
\title{CMPE 211 - Data Structures and Algorithms}
%\setlength\headheight{26pt} 




\date{}
\maketitle
\setcounter{secnumdepth}{0}


Necessary steps for building a recommender system is explained in the course. You can find the material at \url{https://github.com/uzay00/CMPE211}. Based on our discussions,
implement a recommender system from scratch with Java. Use what you have learned in our 
CMPE 211 - Data Structures and Algorithms course.

\paragraph{Part 0} Data
\begin{enumerate}
\item[1P] Choose an appropriate data structure. 
\item[1P] Load MovieLens Data to a nested symbol table.
\end{enumerate}

\paragraph{Part 1} User-based recommendation
\begin{enumerate}
\item[1P] write a \emph{dist()} function
\item[1P] write a \emph{intersection()} function
\item[1P] write a \emph{sim\_distance()} function
\item[2P] write a \emph{topMatches()} function
\item[2P] write a \emph{getRecommendations()} function
\end{enumerate}


\paragraph{Part 2} Item-based recommendation
\begin{enumerate}
\item[1P] write a \emph{transformPrefs()} function
\item[1P] apply Part 1 function to transformed data.
\item[2P] write a \emph{calculateSimilarItems()} function
\item[2P] write a \emph{getRecommendedItems()} function and apply to movielens data

\end{enumerate}

\paragraph{Bonus} Discuss possible research directions based on this recommender system. You may get extra points for your creative thinking for the discussion part of our course. 
\end{document}
